### 2020-02-25 defesa/tex/chapter/numerical.tex
wip

In this section, we describe some new instances which were created with the intention of further analyzing the algorithms developed by our work. We introduce larger instances and try to create cases which our algorithm does not perform as well as it does for the instances CM1-CM9 and AB001-AB120.

>>>>

In this section, we describe some new instances which were created with the intention of further analyzing the algorithms developed by our work.

To generate the demand set, for each point, we had its coordinates follow a normal distribution $\mathcal{N}(0, 1)$. This way, most of the points are expected to be near the origin, making optimal solutions cover bigger portions of the demand set when compared to the previously analyzed instances.
We constructed eight instances with $n=150$ and $m=8$, and generated the ellipse's shapes uniformly randomly in the interval $[0.5, 1.5]$, setting the cost for the $i$-th ellipse as $c_i=a_i\times b_i$, and the weight of every point as $1$.
